---
output: rmarkdown::github_document
---

`algorithmia` : R interface to the [Algorithmia](https://algorithmia.com/) API

The following functions are implemented:

- `algo_api_key`:	Get or set ALGORITHMIA_API_KEY value
- `algo_call`:	Call an Algorithmia algorithm
- `algo_client`:	Initialize a new Algorithmia API client call
- `algo_dir_exists`:	Test if a directory exists
- `algo_dir_list`:	List a directory accessible by the Algorithmia service
- `algo_download_file`:	Read a file from a URI accessible by the Algorithmia service & write to disk
- `algo_file_exists`:	Test if a file exists
- `algo_options`:	Set options for an algorithm call
- `algo_pipe`:	Execute an Algorithmia algorithm call
- `algo_read_file`:	Read a file from a URI accessible by the Algorithmia service

### TODO

- Finish file & dir functions
- Wrap things with `purrr::safely()`
- Craft something elegant for `output=void` option
- Test with more gnarly endpoints
- Finish documentation

### Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/algorithmia")
```

```{r echo=FALSE, message=FALSE, warning=FALSE, error=FALSE}
options(width=120)
```

### Usage

```{r}
library(algorithmia)

# current verison
packageVersion("algorithmia")

```

### Test Results

```{r message=FALSE}
library(algorithmia)
library(testthat)
library(magrittr)
```

```{r}
date()

algo_client() %>%
  algo_call("demo", "Hello", "0.1.1") %>%
  algo_options(30) %>%
  algo_pipe("there", "text")

# Have to provide some assistance to `httr` if the input is not a named list
# and the content type is set to "json"

algo_client() %>%
  algo_call("demo", "Hello", "0.1.1") %>%
  algo_options(30) %>%
  algo_pipe('"there"', "json")

algo_client() %>%
  algo_dir_exists("s3://public-r-data/")

algo_client() %>%
  algo_dir_list("s3://public-r-data/")

algo_client() %>%
  algo_file_exists("s3://public-r-data/ghcran.json")

algo_client() %>%
  algo_read_file("s3://public-r-data/ghcran.json", fmt="parsed") -> cran

str(cran[[1]])

#test_dir("tests/")
```

